\documentclass[authoryear,5p]{elsarticle}

\renewcommand{\today}{}  % Get rid of date on footer
\journal{Ann. Nucl. Energy}

\usepackage[bitstream-charter]{mathdesign} % Use BT Charter font
\usepackage[T1]{fontenc}                   % Use T1 encoding instead of OT1
\usepackage[utf8]{inputenc}                % Use UTF8 input encoding
\usepackage{microtype}                     % Improve typography
\usepackage{amsmath, mathtools}             % AMS Math extensions
\usepackage{booktabs}                      % Improved table spacing
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{breqn}
\usepackage{nicefrac}
\usepackage{multirow}

\usepackage[breaklinks=true]{hyperref}

\usepackage{subcaption}
\usepackage{dblfloatfix}
\usepackage{color}

\usepackage{todonotes}

\usepackage[labelfont=bf]{caption}
\captionsetup[figure]{labelsep=period, name=Figure}
\captionsetup[table]{labelsep=period, name=Table}
\def \figureautorefname {Figure}
\def \algorithmautorefname {Algorithm}

\usepackage[scaled]{beramono}

\usepackage{etoolbox}
\usepackage{listings}
\usepackage{color}

% Algorithm constructs
\usepackage{algorithm} % Provides algorithm environment
\usepackage{algorithmicx}       % Provides algorithmic block
\usepackage{algpseudocode}      % Option of algorithmicx package

\newcommand{\code}[2]{
  \subsection*{#1}
  \lstinputlisting{#2}
}

\def\sectionautorefname{Sec.}
\def\subsectionautorefname{Sec.}
\def\subsubsectionautorefname{Sec.}
\def\tableautorefname{Tab.}
\def\equationautorefname{Eq.}
\def\figureautorefname{Fig.}
\def\algorithmautorefname{Alg.}

% Patch to make equation autoref counter work
\makeatletter
\patchcmd\eq@setnumber{\stepcounter}{\refstepcounter}{}{%
  \errmessage{Patching \noexpand\eq@setnumber failed}%
}
\makeatother

\hypersetup{colorlinks=true,
  pdftitle={The Impact of Inter-Pin Spatial Self-Shielding on Pin-Wise Reaction Rates},
  pdfauthor={William Boyd, Benoit Forget and Kord Smith.}}

\begin{document}

\begin{frontmatter}

\title{A Single-Step Framework to Generate Spatially Self-Shielded Multi-Group Cross Sections from Monte Carlo Transport Simulations}

\author[MITRE]{William Boyd\corref{cor1}}
\ead{wboyd@mitre.org}

\author[MIT]{Benoit Forget\corref{}}
\ead{bforget@mit.edu}

\author[MIT]{Kord Smith\corref{}}
\ead{kord@mit.edu}

\address[MITRE]{MITRE Corporation, 7525 Colshire Drive, McLean, VA 22102, United States}
\address[MIT]{Massachusetts Institute of Technology, Department of Nuclear Science and Engineering, 77 Massachusetts Avenue, Building 24, Cambridge, MA 02139, United States}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{abstract}

\begin{keyword}
Neutron transport, multi-group cross-sections, spatial self-shielding, spatial homogenization
\end{keyword}

\end{frontmatter}

\input{introduction}
\input{single-step}
\input{pin-wise-shielding}
\input{simulation-tools}
\input{benchmarks}
\input{results}
\input{conclusions}
\input{acknowledgements}

\section*{References}
\bibliography{references}
\bibliographystyle{annals}

\end{document}
